Apache Storm

### 2018-02-18 paper.tex
Fixes made according to final request

\section{Stream Processing}
A stream is a continuous flow of data from one point to the other. Stream Processing System works on these data streams, the task of these processing scheme may range from simple transformations to something as complex as event processing. In this present digitized world, people tend to post most of their thoughts and voices about topics on the web. These may be in the form of a long text, generally a webpage called blogs, or as a short post on a social networking site. An example of a social networking site is Twitter. In twitter, people tend to post short views about various things and at any moment there are a number of people posting onto twitter.

@@

\subsection{Stream Processing Models}
There are two types of stream processing models, namely continuous flow model and discretized stream model. \cite{streaming}

\subsubsection{Continuous Stream Processing}

\subsubsection{Discretized Stream Processing}

\section{Apache Storm: Concepts}
\label{sec:concepts}

@@

\subsection{Architecture Overview}
The physical high level architecture of Storm as seen in figure \ref{fig:physicalarc} consists of a single master node and multiple worker nodes. The master node(see later) is the leader of the cluster and is responsible in short for the management of the different parts of the topology. There can only be one master node in a cluster. The worker node on the other hand is responsible for the actual execution of tasks supplied by the user. A user task is defined in storm as a Topology which actually is a directed graph. The vertices of the graph represent the data processing being done and the edges the flow of data. A data stream passed through the topology yields the required processing result as defined by the user.

\begin{figure}
  \begin{center}
    \includegraphics[width=.7\textwidth]{arch.png}
    \caption{High Level Storm Physical Architecture}
    \label{fig:physicalarc}
   \end{center}
\end{figure}

The logical or the runtime architecture of storm is defined within a topology. As seen in figure \ref{fig:logicalarch} shows an example of a topology and consists of vertices and edges, the vertices represent point where either data is generated or some processing to the existing data is done. The edges represent the flow of data, and in a topology, the data is represented in the form of tuples. A vertex can in storm be either a spout or a bolt. A spout is the source of tuples and it injects tuples into the topology, wheras a bolt is a vertice within a topology where the injected tuples are processed.

\begin{figure}
  \begin{center}
    \includegraphics[width=.7\textwidth]{arch.png}
    \caption{High Level Storm run-time or Logical Architecture}
    \label{fig:logicalarch}
   \end{center}
\end{figure}

The logical and physical architectures meet while being deployed in a cluster, the worker nodes are responsible for executing the topology. Every worker spawns a number of processes which run topologies. See later for detailed explanation on how topologies can be divided and executed within a storm cluster.

\subsubsection{Storm Components}
\paragraph{Master node} also called the \textbf{Nimbus} is responsible for the distribution and coordination of the execution of topologies. The Nimbus is the first point where the user submits the defined topology, which is then distributed among the worker nodes. The user submits the code as a jar file to the nimbus, which in turn uses a combination of local disk and the zookeeper to store the topology defined in the jar file.\cite{stormtwitter} The topology thrift objects are stored in the zookeeper, whereas the code itself is stored in the local disk of nimbus.
\paragraph{Worker Node} is responsible for all the heavy lifting required for processing the incoming data stream. A worker node maintains a \textbf{Supervisor} process and multiple worker processes. The number of  worker processes depends upon the storm configurations. A worker process once spawned, starts working for a single topology alone and not for a multiple number of topologies. It creates threads called \textbf{Executors} which take up a tasks to be performed. A task for an executor is the vertex of the Directed graph, ie. either a bolt or a spout. This can be observed in the \ref{fig:workerarch}, where a worker node has multiple worker processes, which in turn has multiple executors running different tasks. 
Even though storm can run multiple topologies, different processes run separate topologies.

The introduction of tasks enables a parallel execution of a number of same bolt or spout node of a topology, whereas the introduction of executors enables us to run different parts of the topology namely bolts and spouts in parallel.\cite{stormtwitter}. It is worth noting that these different parts of the topology, namely bolts and spouts can be executing within a single worker process in different executors, or can also be in different executors across different worker nodes.

@@

\subsubsection{Topology}
\paragraph{Topology} is a directed graph where the vertices represent computation and the edges represent the data flow. Another important thing about topologies in Storm is that they are allowed to have cycles. Figure \ref{fig:topo} shows a basic Storm Topology, which consists of Spouts and Bolts. Spouts are the Sources of tuples in a Topology whereas Bolts are the units which process these generated tuples. The user first submits the topology to the Apache Storm Nimbus, which consults with each of the available Supervisors in the worker nodes and assigns each of them with tasks related to the topology.

\paragraph{Spouts} are the entry point for any data in the Storm Topology. As shown in the figure \ref{fig:topo} spouts take data from external source and emits them into the topology as tuples. The input source could be a Heterogenous data source.

\paragraph{Bolts} are the processing entities of a Topology. It receives raw tuples emitted by spouts or processed tuples sent by another bolt and sends it down the pipe after it has completed its processing.

@@

\subsection{Storm Features}
\subsubsection{Fault Tolerance and Resilience}
\label{sec:resilience}
Apache storm offers fault tolerance and resilience mechanisms with out of the box support and is tolerant against different types of failures. Nimbus, being the main master node, is in-charge of all the other worker nodes. Under the circumstance that a worker node fails, Nimbus re-spawns a worker node and assigns the tasks to this node. If the nimbus itself fails, the nimbus is not re-started automatically, but the worker nodes do not stop processing the stream. The nimbus can be later on restarted manually. During this phase, if a worker fails, it will not be restarted. The supervisor is also an active element within the Storm Architecture and keeps the Nimbus posted about it's current status. The \textbf{heartbeat} event is scheduled to run every 15 seconds and it reports to the Nimbus that the worker node is alive. \cite{stormtwitter}

@@

\paragraph{Figure} \ref{fig:acker} shows the Acker bolt integration with the storm topology. It keeps track of the tuple flow starting from the point where it has been injected into the topology till it leaves the topology. After the tuple has left the topology, an \textbf{ack} is sent to the Spout, at this point, it can decide to remove the Tuple from memory.

\section{Stream Processing: Design Considerations}
A stream is a continuous flow of data from one point to the other. A Stream Processing system works on these data streams, the work may just be simple transformations, but could also be as complex as predictive analysis. A stream processing system depending on the nature of application has different requirements.

Let us consider the news feed service provided by any social networking site, we know that in any of these websites we can read posts created by our friends or family and it does not matter if we see them at the very instance they post. But, there are cases such as a stream of purchases, where we want the data to be visible as soon as available separate design considerations should be made. This section focuses on the various considerations that are to be made while designing a stream processing system, specifically using Apache Storm.

\subsection{System Architecture}
As discussed above, a data processing stream has different requirements and according to these various requirements, the System can be modified to suit these needs. The major two System architectures currently available are the Lambda Architecture and the Lambda-less (or Kappa) Architecture.

\subsubsection{Lambda-less Architecture}
\paragraph{Kappa Architecture} or the lambda-less Architecture is a System Architecture concept where there are only two layers, namely Speed Layer and Serving Layer.The data input to the system is processed at real time to retrieve the results at real time. The major advantage of this type of system is that there is minimum latency. This type of architecture is more suitable in cases where an accurate view of the data is preferable without a lot of delay. Cash transactions might be one of these cases where a minimum delay for transaction visualization is suitable added the calculations done on these data sets are properly formulated as well.

This architecture can be considered has an advantage over the lambda architecture (described later) , that a single code base is to be maintained throughout the life of the software. But, any apparent change to the code base results in a need for a duplicate cluster to analyze the data again and update the view. A working example of this architecture is presented in the section \ref{sec:usecase}. One may use this architecture over the lambda architecture when both the algorithms for the batch processing and stream processing are the same and the requirements mentioned above are the major focus.

\subsubsection{Lambda Architecture}
\paragraph{Lambda Architecture} is a data processing Architecture designed to handle high volume data utilizing the best of both batch and stream processing. Figure \ref{fig:lambda} shows a generic architecture principle for Lambda Architecture. The three composed layers are: Speed Layer, Batch Layer and Serving Layer. The batch processing layer provides an accurate view of the data but provides results in batches, whereas the speed layer provides current data visualizations which may or may not be accurate depending upon the algorithm. The serving layer utilizes both the speed layer as well as the batch layer to fulfill the request to a query.

Lambda architecture requires maintanence of two separate systems as well as code bases, and thus may result in higher cost. But, the added advantage is that the batch processing layer code can be optmized for the given data set to obtain better results. An example scenario could be a specialized news feed which requires machine learning algorithms to customize the user experience. The Speed layer could be used to deliver recent news, but the batch layer could use machine learning to produce the customized feed. An added advantage is that Lambda architecture holds the input data unchanged.\cite{lambdastorm}

\begin{figure}
  \begin{center}
    \includegraphics[width=.7\textwidth]{lambda.png}
    \caption{Lambda Architecture}
    \label{fig:lambda}
   \end{center}
\end{figure}

\subsection{Topology Design Considerations}
A storm topology design with the spouts and bolts and affects the overall system thus should be properly considered. A spout should inject data into the topology from external sources whereas the bolt should be a smallest implementable task. A storm topology should also be considered with various considerations in mind:

\subsubsection{Scalability:} A designed topology should be considered with scalability in mind. The major question is what configuration of bolts enables us to process greater amount of data at real time. Let us consider a simple example of word count topology which counts the repetition of words and ranks the most used words. It can be performed by simply including a spout and two bolts, the first of which to count the number of words and the second to aggregate and rank it (see fig. \ref{fig:ranking} Topology Setup 1).
Since we should have only one instance of Aggregator, to be able to get the aggregated result, in cases of increased data load, the number of rolling count bolts can be increased, but the Aggregation Bolt cannot be increases thus adding increased load at this node. To relax the demand on this node, we can introduce another bolt, the Intermediate Ranking Bolt, which is responsible for ranking the words at certain predefined intervals and passes the intermediate ranks to the aggregator. This reduces load on the Aggregator since we can increase the intermediate ranking bolts to cope with the increased load.

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{ranking.png}
    \caption{Possible Topologies for Word Count and Ranking}
    \label{fig:ranking}
   \end{center}
\end{figure}

\subsubsection{Resilience:} Apache storm includes APIs which allow users to develop solutions which are resilient in nature. Using the acker bolt as shown in figure \ref{fig:acker}, users can track the progress of the tuple injected into the system. Thus, writing a spout which can replay the tuple in case of failures allows us to guarantee the processing of data. For additional details please follow Section \ref{sec:resilience}.

\subsubsection{Interoperability:} The designed topology should be interoperable with different sources of data, and by default should work out of the box by adding simply other Spouts in the topology. This also amounts to the maintainability of the code.

@@

\paragraph{This} is not the only possible solution, there are multiple other tools such as \textbf{Spark Streaming}, \textbf{Samza}, etc. but this paper concentrates Apache Storm as it is in the spotlight of this paper, for further details regarding other available tools and their comparisons with Apache Storm, please consider the section \ref{sec:othertools} for further details.

@@

The only spout available in this example uses Twitter Hosebird Client (\url{https://github.com/twitter/hbc}) to connect to Twitter Streaming Server and consume the Tweets generated in real time. Whereas the Bolts were programmed in java and the code can be viewed in \url{https://github.com/hakku276/storm-sentiment-analysis}.

@@

\section{Other Tools}
 \label{sec:othertools}
Stream processing is a topic under constant focus at present and a lot of tools as well as models have been designed and created to support it. This section makes a comparison of the available widely accepted tools today. The available tools are mentioned below in brief such as:

@@

 \subsection{Comparison between Storm, Spark and Samza}
This sub section compares the three most widely used tools for Stream Processing, i.e. Storm, Spark and Samza.

@@

 \subsubsection{Fault Tolerance}
As stream processing systems run for extended periods, it is quite necessary that these are able to handle various kinds of faults and still keep processing data as they enter the system. The fault tolerance model for Storm has been extensively described in section \ref{sec:resilience}. Similarly, Spark Streaming and Apache Samza also use various techniques to resolve issues while deployed. Spark Streaming uses write ahead logs(journals) to keep track of all the data operation, and during failure of a worker, the worker is restarted and a state restore is done by reading the logs. This ensures that the data is processed as required. In comparison to Apache Storm, Storm continues to process incoming tuples even when the master node fails, but in Spark, the worker nodes stop working when the master node fails until a new leader starts. This is an added bonus to Storm, since a failed master manual restart would reinstate the state of the system without many changes.

\begin{figure}
\begin{center}
\includegraphics[width=.75 \textwidth]{comparisiongraph.png}
\caption{Performance Comparision between Apache Storm, Apache Flink and Spark Streaming \cite{benchmark}}
\label{fig:comparisiongraph}
\end{center}
\end{figure}

@@

 \section{Discussion}
Apache Storm acts as a real time stream processing tool which is capable of computing results with high reliability and minimum latency. The tool is comparatively easy to setup and configure, with out of the box configurations which is production ready. The storm API is relatively simple and does not have a complicated method calls, the programming is based on event driven programming and since storm supports read and writes based on standard IO, utilizing previously written code could be relatively easier than in the other available tools. Data is currently being generated and consumed at an unprecedented rate, thus stream processing technologies is a requirement and is gaining popularity and attention. With all the various tools available, one can decide on which tool best suites ones needs. According to the benchmarks, if minimum latency is required, Apache Storm or Apache Flink or any system with Continuous data flow model should be preferred. Whereas if high throughput is required with a non strict latency criteria, Spark streaming could prove to be a better option.

>>>>

\section{Apache Storm: Concepts}
\label{sec:concepts}
A stream is a continuous flow of data from one point to the other. Stream Processing System works on these data streams, the task of these processing scheme may range from simple transformations to something as complex as event processing. In this present digitized world, people tend to post most of their thoughts and voices about topics on the web. These may be in the form of a long text, generally a webpage called blogs, or as a short post on a social networking site. An example of a social networking site is Twitter. In twitter, people tend to post short views about various things and at any moment there are a number of people posting onto twitter.

@@

@@

\subsection{Architecture Overview}
The physical high level architecture of Storm as seen in figure \ref{fig:physicalarc} consists of a single master node and multiple worker nodes. The master node(see later) is the leader of the cluster and is responsible in short for the management of the different parts of the topology. There can only be one master node in a cluster. The worker node on the other hand is responsible for the actual execution of user logic. Storm requires at least one worker node to execute the user logic and apart from it a Zookeeper to keep track of the state of the various nodees in the cluster.

\begin{figure}
  \begin{center}
    \includegraphics[width=.7\textwidth]{arch.png}
    \caption{Storm Physical Architecture}
    \label{fig:physicalarc}
   \end{center}
\end{figure}

The logical or the runtime architecture of storm is defined in storm via the abstraction of a topology. Topoloyg is a directed graph, with data flows and transformations to the flowing data. As seen in figure \ref{fig:topo} shows an example of a topology and consists of vertices and edges, the edges represent the flow of data whereas the vertices represent point where either data is generated or some processing to the existing data flowing throw it.

\subsubsection{Storm Components}
\paragraph{Master node} also called the \textbf{Nimbus} is responsible for the distribution and coordination of the execution of topologies. The Nimbus is the first point where the user submits the defined topology, which is then distributed among the worker nodes. The user submits the code as a jar file to the nimbus, nimbus then uses a combination of local disk and the zookeeper to store the topology defined in the jar file.\cite{stormtwitter} The topology thrift objects are stored in the zookeeper, whereas the code itself is stored in the local disk of nimbus. It then assigns the task to the worker nodes to execute selected parts of the topology.
\paragraph{Worker Node} is responsible for all the execution required for processing the incoming data stream. A worker node maintains a \textbf{Supervisor} process and multiple worker processes. The number of  worker processes depends upon the storm configurations and the number of woker nodes available. A worker process once spawned, starts working for a single topology alone and not for a multiple number of topologies. It creates threads called \textbf{Executors} which take up a tasks to be performed. A task for an executor is the vertex of the Directed graph. This can be observed in the \ref{fig:workerarch}, where a worker node has multiple worker processes, which in turn has multiple executors running different tasks. 
Even though storm can run multiple topologies, different processes may run separate topologies.

@@

\subsubsection{Topology}
\paragraph{Topology} is a directed graph where as mentioned before the vertices represent computation and the edges represent the data flow. It is wise to note that topologies in Storm are allowed to have cycles. The data in storm is abstracted using a Data type called the Tuple. A tuple is a list of ordered element, which as well contain names. The vertices of the topology can be abstracted into two different types, first the bolt and second the spout. \textbf{Spout} is the source of tuples into the topology whereas \textbf{Bolt} is a point in the topology where the tuples are transformed. A bolt typically does a simple transformation, in order to obtain a complex transformation, chaining of bolts can be done.

The figure \ref{fig:topo} shows a basic Storm Topology with a single spout and three different bolts. The spout reads data from external sources, either homogenous or heterogenous and passes on to the bolts, according to the figure Bolt 1 and Bolt 2. Bolt 1 and Bolt 2 perform simple transformations and send the results to Bolt 3, which finalizes the data transformation and sends it to the Target. A topology as can be noted in the figure might have multiple instances of Bolts or Spouts running, which allows the scalability of the total system.

@@

\paragraph{Multiple instances} of the same bolt is available within a topology, thus, Storm allows one to partition the data stream to the bolts, termed as Stream Grouping. There are eight available built-in stream groupings which can be used and custom extensions can be made according to the needs of the system.\footnote{\url{http://storm.apache.org/releases/1.1.0/Concepts.html}} The common built-in groupings are:

\begin{enumerate}
\item{Shuffle Grouping} : Random distribution of the tuples among the target nodes. Load balancing can be achieved using this grouping.
\item{Fields Grouping} : The tuples are partitioned by the value of a field. All the tuples with the same value of a specific field are routed to the same instance of the bolt. Can be used if a state of the bolt depends on the value of a field within the tuple.
\item{All Grouping} : The tuples are replicated to every instance of the bolt.
\item{Global Grouping} : The tuples are sent only to a single instance of the bolt.
\end{enumerate}

Each tuple is produced and consumed by bolts, but actual communication happens between the Worker processes. Each worker process has a Send thread and a Receive Thread which is responsible for handling the communication. As seen in figure \ref{fig:communication}, the Worker Receive thread receives messages from the global buffer and demultiplexes it to the respective tasks running in the User thread pool. Each User thread contains two message queues associated with it, the in-queue where incoming data is stored and the out-queue where the outgoing data is stored. The user thread, takes messages from the queue, processes them and sends them to the out queue. The data in the out queue is processed by the send queue and then passed on to the Worker Send Thread to be communicated into the network.

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{topo.png}
    \caption{Generic Storm Topology}
    \label{fig:communication}
   \end{center}
\end{figure}

\subsection{Storm Features}
Apache Storm has many features, some of them have been described in this section.
\subsubsection{Scalable}
\paragraph{Apache Storm} is a distributed system, and thus highly scalable. Adding of worker nodes in a storm is possible to increase the computational capacity of the total system. The concept of bolts with limited computations, allows one to increase the number of bolts performing a single task. For example, in a scenario where Bolt 1 parses text and Bolt 2 just counts occurrances, it is clear that Bolt 1 takes more time to process data rather than Bolt 2. So, increasing the number of Bolt 1 could be a better option in terms of scalability.

\subsubsection{Simple API}
\paragraph{Storm} provides a simple API for building on top of the pre-defined abstractions. Listing \ref{lst:spout} shows a bare bone implementation of a Spout. The Spout class extends the BaseRichSpout and implements only four methods, namely, declareOutputFields to declare the output fields this spout will be producing, open to handle initialization phase and close to handle the destroy phase and nextTuple to generate the next tuple. The API is similarly simple for implementing a Bolt. The complete detail of the API is out of the scope of this report and can be obtained from the official Storm documentation

\begin{lstlisting}[float,caption=Bare Spout Implementation,label=lst:spout]
public class TwitterFeedSpout extends BaseRichSpout {
	@Override
	public void declareOutputFields(OutputFieldsDeclarer declarer) {
	}

	@Override
	public void open(Map conf, TopologyContext context, 
	SpoutOutputCollector collector) {
	}

	@Override
	public void nextTuple() {
	}

	@Override
	public void close() {
	}
}
\end{lstlisting}

Another feature of the Storm API is that it supports multiple languages using JSON based protocol over Standard IO\footnote{\url{http://storm.apache.org/about/multi-language.html}}. This enables code reusability in most cases and makes it easier to port code into storm.

\subsubsection{Fault Tolerance and Resilience}
\label{sec:resilience}
\paragraph{Apache storm} offers fault tolerance and resilience mechanisms with out of the box support and is tolerant against different types of failures. Nimbus, being the main master node, is in-charge of all the other worker nodes. Under the circumstance that a worker node fails, Nimbus re-spawns a worker node and assigns the tasks to this node. If the nimbus itself fails, the nimbus is not re-started automatically, but the worker nodes do not stop processing the stream. The nimbus can be later on restarted manually. During this phase, if a worker fails, it will not be restarted. The supervisor is also an active element within the Storm Architecture and keeps the Nimbus posted about it's current status. The \textbf{heartbeat} event is scheduled to run every 15 seconds and it reports to the Nimbus that the worker node is alive. \cite{stormtwitter}

@@

\paragraph{Figure} \ref{fig:acker} shows the Acker bolt integration with the storm topology. It keeps track of the tuple flow starting from the point where it has been injected into the topology till it leaves the topology. After the tuple has left the topology, an \textbf{ack} is sent to the Spout, at this point, it removes the entry from memory.

@@

\paragraph{This} is not the only possible solution, there are multiple other tools such as \textbf{Spark Streaming}, \textbf{Samza}, etc. but this paper concentrates Apache Storm as it is in the spotlight of this paper, for further details regarding other available tools and their comparisons with Apache Storm, please consider the section \ref{sec:toolcomparision} for further details.

@@

The only spout available in this example uses Twitter Hosebird Client (\url{https://github.com/twitter/hbc}) to connect to Twitter Streaming Server and consume the Tweets generated in real time. Whereas the Bolts were programmed in java and the complete code can be viewed in \url{https://github.com/hakku276/storm-sentiment-analysis}. A short extract how the topology was created can be seen in listing  \ref{lst:toposetup}. We can see that a spout has been declared in line 2, then a parser bolt and finally a aggregator bolt with parallelism 1. It is then submitted to storm (nimbus).

\begin{lstlisting}[float,caption=Bare Spout Implementation,label=lst:toposetup]
TopologyBuilder builder = new TopologyBuilder();
builder.setSpout("spout", new TwitterFeedSpout(tags));
builder.setBolt("parse", new TweetParseBolt())
	.shuffleGrouping("spout");
builder.setBolt("aggregation", new TwitterAggregationBolt(), 1)
	.shuffleGrouping("parse");
StormSubmitter.submitTopology("SentimentAnalyzer", config, 
	builder.createTopology());
\end{lstlisting}

@@

\section{Comparision to Related Work}
 \label{sec:toolcomparision}
Stream processing is a topic under constant focus at present and a lot of tools as well as models have been designed and created to support it. This section makes a comparison of the available widely accepted tools today.

@@

@@

 \subsubsection{Fault Tolerance}
As stream processing systems run for extended periods, it is quite necessary that these are able to handle various kinds of faults and still keep processing data as they enter the system. The fault tolerance model for Storm has been extensively described in section \ref{sec:resilience}. In cases of worker failure, as described earlier, Storm restarts the worker and if a tuple that is being processed by this node was lost, is again replayed. Similarly, Spark Streaming and Apache Samza also use various techniques to resolve issues while deployed. Spark Streaming uses parallel worker recovery which is possible with the help of RDDs and Apache Samza uses checkpointing to restore a failed state. Due to the parallel recovery of Spark Streaming, in my opinion it proves better in worker failure resilience, since Storm can recognize that a node has failed and can restart it, but it cannot know a tuple has been lost until the tuple has timed out. Time outs take extra time and results in slower processing.

In case of master node failure, Storm worker node continues to process incoming tuples, but in Spark, the worker nodes stop working when the master node fails until a new leader starts. This is an added bonus to Storm, since a failed master manual restart would reinstate the state of the system without changes. This is a better resilience feature than provided by Spark Streaming.

\begin{figure}
\begin{center}
\includegraphics[width=0.85\textwidth]{comparisiongraph.png}
\caption{Performance Comparision between Apache Storm, Apache Flink and Spark Streaming \cite{benchmark}}
\label{fig:comparisiongraph}
\end{center}
\end{figure}

@@

 \section{Discussion}
Apache Storm acts as a real time stream processing tool which is capable of computing results with high reliability and minimum latency. The tool is comparatively easy to setup and configure, with out of the box configurations which is production ready. The API is as well relatively simple and does not have a complicated method calls, the programming is based on event driven programming and since storm supports read and writes based on standard IO, utilizing previously written code could be relatively easier than in the other available tools. Data is currently being generated and consumed at an unprecedented rate, thus stream processing technologies is a requirement and is gaining popularity and attention. With all the various tools available, one can decide on which tool best suites ones needs. According to the benchmarks, if minimum latency is required, Apache Storm or Apache Flink or any system. Whereas if high throughput is required with a non strict latency criteria, Spark streaming could prove to be a better option.
